### 2016-06-30 R/ITHIM.Rmd
Update to ITHIM.Rmd

>>>>

```{r matrices}
nonTravelMETs <- rbind(0,rbind(0,cbind(parameters$mean_mets[7:12], parameters$mean_mets[1:6])))
nonTravelMETsNormalized <- nonTravelMETs/nonTravelMETs[3,2]
meanNonTravelMETs <- nonTravelMETs[3,2]

```{r plotMatrix}
D <- melt(nonTravelMETsNormalized)
ggplot(D, aes(Var2, value)) + geom_bar(aes(fill=Var1), stat = "identity", position = "dodge")
```

```{r fooFunction}

probActive <- 0.15

METQuintiles <- mapply(getMETQuintiles, nonTravelMETsNormalized*nonTravelMETs, MoreArgs = list(cv = cv0_mets, p = probActive, size = 1e4), SIMPLIFY = FALSE)
